Pteropod biomarker analysis

### 2018-03-01 eval.Rmd
trying to fix on shiny server

library(tidyverse)
library(vegan)
# library(ggord)
library(scales)
library(effects)
library(shiny)

@@

RDA triplot of biomarkers and environmental data
```{r, fig.height = 4, fig.width = 5, eval = F}
dat_frm <- dat %>% 
  mutate(
    CAT = ifelse(is.nan(CAT), mean(CAT, na.rm = TRUE), CAT)
  ) %>% 
  data.frame %>% 
  column_to_rownames('CTD')

>>>>

library(tidyverse)
library(vegan)
library(ggord)
library(scales)
library(effects)
library(shiny)

@@

RDA triplot of biomarkers and environmental data
```{r, fig.height = 4, fig.width = 5, eval = T}
dat_frm <- dat %>% 
  mutate(
    CAT = ifelse(is.nan(CAT), mean(CAT, na.rm = TRUE), CAT)
  ) %>% 
  data.frame %>% 
  column_to_rownames('CTD')
